Results

### 2018-03-30 02_analysis.Rmd
Output figures and tables

tidy_diffs <- function(diffs_pairs) {
  diffs_pairs %>% 
    gather(pair, value) %>% 
    group_by(pair) %>% 
    summarise(mean = mean(value),
              median = median(value),
              q2.5 = quantile(value, probs = 0.025),
              q5 = quantile(value, probs = 0.05),
              q25 = quantile(value, probs = 0.25),
              q75 = quantile(value, probs = 0.75),
              q95 = quantile(value, probs = 0.95),
              q97.5 = quantile(value, probs = 0.975),
              p.greater0 = mean(value > 0),
              p.less0 = mean(value < 0))
}
```

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  janitor::adorn_totals(where = "row") %>% 
  pandoc.table()
```

@@

```{r tbl-descriptive-statistics, results="asis", warning=FALSE}
vars_to_summarize <- tribble(
  ~variable, ~clean_name,
  "donate_likely", "Likelihood of donation",
  "donate_likely_bin", "Likelihood of donation (binary)",
  "amount_donate", "Amount hypothetically donated ($)",
  "favor_humanitarian", "Prior favorability towards humanitarian NGOs",
  "favor_humanitarian_bin", "Prior favorability towards humanitarian NGOs (binary)",
  "favor_human_rights", "Prior favorability towards human rights NGOs",
  "favor_human_rights_bin", "Prior favorability towards human rights NGOs (binary)",
  "favor_development", "Prior favorability towards development NGOs",
  "favor_development_bin", "Prior favorability towards development NGOs (binary)",
  "give_charity", "Frequency of charitable donations",
  "volunteer", "Volunteered in past 12 months",
  "political_knowledge", "Frequency of following public affairs",
  "ideology", "Political views",
  "education", "Education",
  "religiosity", "Frequency of attending religious services",
  "gender", "Gender",
  "income", "Income",
  "age", "Age",
  "check1", "Attention check 1",
  "check2", "Attention check 2"
)

@@

results_summary_stats %>% knitr::kable()
```

@@

conditions_summary_clean %>% pandoc.table()
```

@@

conditions_summary_clean %>% 
  select(1:3) %>% 
  slice(-n()) %>% 
  bind_cols(interpretation) %>% 
  pandoc.table()
```

@@

```{r tbl-models-amount, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

@@

```{r plot-all-amount-medians, fig.width=8, fig.height=6}
((plot_amount_c + 
   labs(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_amount_ci) | plot_amount_cif
```

@@

```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
((plot_diffs_c + 
   labs(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_ci) | plot_diffs_cif
```

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
  pandoc.table(missing = "—", 
               caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions')
```

@@

```{r tbl-models-likely, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %>% 
  print_hux()
```

@@

```{r plot-all-likely-medians, fig.width=8, fig.height=6}
((plot_likely_c + 
   labs(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_likely_ci) | plot_likely_cif
```

@@

```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
((plot_diffs_likely_c + 
   labs(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_likely_ci) | plot_diffs_likely_cif
```

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `P(m > 0)` = p.greater0, `P(m < 0)` = p.less0) %>% 
  pandoc.table(missing = "—", 
               caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions')
```

>>>>

tidy_diffs <- function(diffs_pairs) {
  diffs_pairs %>% 
    gather(pair, value) %>% 
    group_by(pair) %>% 
    summarise(mean = mean(value),
              median = median(value),
              q2.5 = quantile(value, probs = 0.025),
              q5 = quantile(value, probs = 0.05),
              q25 = quantile(value, probs = 0.25),
              q75 = quantile(value, probs = 0.75),
              q95 = quantile(value, probs = 0.95),
              q97.5 = quantile(value, probs = 0.975),
              p.greater0 = mean(value > 0),
              p.less0 = mean(value < 0),
              p.diff.not0 = ifelse(median > 0, p.greater0, p.less0))
}
```

# Miscellaneous details

## Average time to complete survey

```{r avg-time}
results %>% summarize(min = min(duration),
                      max = max(duration),
                      mean = mean(duration),
                      sd = sd(duration),
                      median = median(duration))
```

## Attention check #2

```{r attention-check-2}
results %>% count(attention2_correct)
```

@@

```{r check-conditions, results="asis"}
results %>% count(crackdown, issue, funding) %>% 
  rename(Crackdown = crackdown, Issue = issue, Funding = funding) %>% 
  janitor::adorn_totals(where = "row") %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Balance of experimental conditions {#tbl:experimental-conditions}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-experimental-conditions.md"))
```

@@

```{r tbl-descriptive-statistics, results="asis", warning=FALSE}
vars_to_summarize <- tribble(
  ~variable, ~clean_name,
  "donate_likely", "Likelihood of donation",
  "donate_likely_bin", "Likelihood of donation (binary)",
  "amount_donate", "Amount hypothetically donated ($)",
  "gender", "Gender",
  "age", "Age",
  "income", "Income",
  "education", "Education",
  "religiosity", "Frequency of attending religious services",
  "ideology", "Political views",
  "political_knowledge", "Frequency of following public affairs",
  "give_charity", "Frequency of charitable donations",
  "volunteer", "Volunteered in past 12 months",
  "favor_humanitarian", "Prior favorability towards humanitarian NGOs",
  "favor_humanitarian_bin", "Prior favorability towards humanitarian NGOs (binary)",
  "favor_human_rights", "Prior favorability towards human rights NGOs",
  "favor_human_rights_bin", "Prior favorability towards human rights NGOs (binary)",
  "favor_development", "Prior favorability towards development NGOs",
  "favor_development_bin", "Prior favorability towards development NGOs (binary)",
  "check2", "Attention check 2"
)

@@

results_summary_stats %>% 
  select(-N) %>% 
  pandoc.table.return(caption = "Descriptive statistics {#tbl:descriptive-stats}",
                      split.cell = 80, split.table = Inf) %T>% 
  cat(file = file.path(here(), "output", "tables", "tbl-descriptive-stats.md")) %>% 
  cat()
```

@@

conditions_summary_clean %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Average likelihood and amount donated across experimental conditions {#tbl:avg-results}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-avg-results.md"))
```

@@

conditions_summary_clean %>% 
  select(1:3) %>% 
  slice(-n()) %>% 
  bind_cols(interpretation) %T>% 
  pandoc.table() %>% 
  pandoc.table.return(caption = "Combinations of coefficients to add to determine means across experimental conditions {#tbl:coefficients-to-add}") %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-coefficients-to-add.md"))
```

@@

```{r tbl-models-amount, warning=FALSE, results="asis"}
huxreg(m_amount_c, m_amount_ci, m_amount_cif, 
       m_amount_c_full, m_amount_ci_full, m_amount_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-amount.md"))
```

@@

```{r plot-all-amount-medians, fig.width=8, fig.height=6}
((plot_amount_c + 
   labs(title = "Median donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_amount_ci) | plot_amount_cif

((plot_amount_c / plot_amount_ci) | 
    plot_amount_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.pdf"),
         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-medians.png"),
         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-amount-diffs, fig.width=8, fig.height=6}
((plot_diffs_c + 
   labs(title = "Differences in median amount donated in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_ci) | plot_diffs_cif

((plot_diffs_c / plot_diffs_ci) | 
    plot_diffs_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "amount-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-all-amount-diffs, results="asis"}
bind_rows(diffs_coef_pairs_detail_c,
          diffs_coef_pairs_detail_ci,
          diffs_coef_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between amounts donated in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-amount-diffs.md"))
```

@@

```{r tbl-models-likely, warning=FALSE, results="asis"}
huxreg(m_likely_c, m_likely_ci, m_likely_cif, 
       m_likely_c_full, m_likely_ci_full, m_likely_cif_full,
       coefs = clean_coefs_named,
       statistics = model_stats_bayes,
       stars = NULL) %T>% 
  print_hux() %>% 
  to_md(max_width = 100) %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-models-likelihood.md"))
```

@@

```{r plot-all-likely-medians, fig.width=8, fig.height=6}
((plot_likely_c + 
   labs(title = "Median likelihood of donation in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown around each point")) / 
   plot_likely_ci) | plot_likely_cif

((plot_likely_c / plot_likely_ci) | 
    plot_likely_cif + labs(caption = "90% credible intervals shown around each point")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.pdf"),
         width = 8, height = 4, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-medians.png"),
         width = 8, height = 4, units = "in", type = "cairo", dpi = 300)
```

@@

```{r plot-all-likely-diffs, fig.width=8, fig.height=6}
((plot_diffs_likely_c + 
   labs(title = "Differences in donation likelihood in control and crackdown groups,\nconditioned by other experimental groups",
        subtitle = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) / 
   plot_diffs_likely_ci) | plot_diffs_likely_cif

((plot_diffs_likely_c / plot_diffs_likely_ci) | 
    plot_diffs_likely_cif + labs(caption = "90% credible intervals shown in black. Solid vertical line = median; dotted vertical line = 0")) %T>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.pdf"),
         width = 8, height = 5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "likelihood-diffs.png"),
         width = 8, height = 5, units = "in", type = "cairo", dpi = 300)
```

```{r tbl-all-likely-diffs, results="asis"}
bind_rows(diffs_coef_likely_pairs_detail_c,
          diffs_coef_likely_pairs_detail_ci,
          diffs_coef_likely_pairs_detail_cif) %>% 
  select(Issue = issue, Funding = funding, 
         `No crackdown − crackdown (median)` = median, 
         `p(∆ > 0)` = p.greater0, `p(∆ < 0)` = p.less0, `p(∆ ≠ 0)` = p.diff.not0) %>% 
  pandoc.table.return(missing = "—", 
                      caption = 'Median difference between likelihood to donate in "no crackdown" (control) and "crackdown" conditions') %T>%
  cat() %>% 
  cat(file = file.path(here(), "output", "tables", "tbl-likelihood-diffs.md"))
```
